### 2016-10-12 paper.tex
Update on Overleaf.

\documentclass{article}

% if you need to pass options to natbib, use, e.g.:
% \PassOptionsToPackage{numbers, compress}{natbib}
% before loading nips_2016
%
% to avoid loading the natbib package, add option nonatbib:
% \usepackage[nonatbib]{nips_2016}

\usepackage{nips_2016}

% to compile a camera-ready version, add the [final] option, e.g.:
% \usepackage[final]{nips_2016}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography

\title{Formatting instructions for NIPS 2016}

% The \author macro works with any number of authors. There are two
% commands used to separate the names and addresses of multiple
% authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to
% break the lines. Using \AND forces a line break at that point. So,
% if LaTeX puts 3 of 4 authors names on the first line, and the last
% on the second line, try using \AND instead of \And before the third
% author name.

\author{
  David S.~Hippocampus\thanks{Use footnote for providing further
    information about author (webpage, alternative
    address)---\emph{not} for acknowledging funding agencies.} \\
  Department of Computer Science\\
  Cranberry-Lemon University\\
  Pittsburgh, PA 15213 \\
  \texttt{hippo@cs.cranberry-lemon.edu} \\
  %% examples of more authors
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \AND
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
}

\begin{document}
% \nipsfinalcopy is no longer used

\maketitle

\begin{abstract}
  The abstract paragraph should be indented \nicefrac{1}{2}~inch
  (3~picas) on both the left- and right-hand margins. Use 10~point
  type, with a vertical spacing (leading) of 11~points.  The word
  \textbf{Abstract} must be centered, bold, and in point size 12. Two
  line spaces precede the abstract. The abstract must be limited to
  one paragraph.
\end{abstract}

\section{Submission of papers to NIPS 2016}

\textbf{There is a new style file for papers submitted in 2016!}

NIPS requires electronic submissions.  The electronic submission site
is
\begin{center}
  \url{https://cmt.research.microsoft.com/NIPS2016/}
\end{center}

Please read carefully the instructions below and follow them
faithfully.

\subsection{Style}

Papers to be submitted to NIPS 2016 must be prepared according to the
instructions presented here. Papers may only be up to eight pages
long, including figures. Since 2009 an additional ninth page
\emph{containing only acknowledgments and/or cited references} is
allowed. Papers that exceed nine pages will not be reviewed, or in any
other way considered for presentation at the conference.

The margins in 2016 are the same as since 2007, which allow for
$\sim$$15\%$ more words in the paper compared to earlier years.

Authors are required to use the NIPS \LaTeX{} style files obtainable
at the NIPS website as indicated below. Please make sure you use the
current files and not previous versions. Tweaking the style files may
be grounds for rejection.

\subsection{Retrieval of style files}

The style files for NIPS and other conference information are
available on the World Wide Web at
\begin{center}
  \url{http://www.nips.cc/}
\end{center}
The file \verb+nips_2016.pdf+ contains these instructions and
illustrates the various formatting requirements your NIPS paper must
satisfy.

The only supported style file for NIPS 2016 is \verb+nips_2016.sty+,
rewritten for \LaTeXe{}.  \textbf{Previous style files for \LaTeX{}
  2.09, Microsoft Word, and RTF are no longer supported!}

The new \LaTeX{} style file contains two optional arguments:
\verb+final+, which creates a camera-ready copy, and \verb+nonatbib+,
which will not load the \verb+natbib+ package for you in case of
package clash.

At submission time, please omit the \verb+final+ option. This will
anonymize your submission and add line numbers to aid review.  Please
do \emph{not} refer to these line numbers in your paper as they will
be removed during generation of camera-ready copies.

The file \verb+nips_2016.tex+ may be used as a ``shell'' for writing
your paper. All you have to do is replace the author, title, abstract,
and text of the paper with your own.

The formatting instructions contained in these style files are
summarized in Sections \ref{gen_inst}, \ref{headings}, and
\ref{others} below.

\section{General formatting instructions}
\label{gen_inst}

The text must be confined within a rectangle 5.5~inches (33~picas)
wide and 9~inches (54~picas) long. The left margin is 1.5~inch
(9~picas).  Use 10~point type with a vertical spacing (leading) of
11~points.  Times New Roman is the preferred typeface throughout, and
will be selected for you by default.  Paragraphs are separated by
\nicefrac{1}{2}~line space (5.5 points), with no indentation.

The paper title should be 17~point, initial caps/lower case, bold,
centered between two horizontal rules. The top rule should be 4~points
thick and the bottom rule should be 1~point thick. Allow
\nicefrac{1}{4}~inch space above and below the title to rules. All
pages should start at 1~inch (6~picas) from the top of the page.

For the final version, authors' names are set in boldface, and each
name is centered above the corresponding address. The lead author's
name is to be listed first (left-most), and the co-authors' names (if
different address) are set to follow. If there is only one co-author,
list both author and co-author side by side.

Please pay special attention to the instructions in Section \ref{others}
regarding figures, tables, acknowledgments, and references.

\section{Headings: first level}
\label{headings}

All headings should be lower case (except for first word and proper
nouns), flush left, and bold.

First-level headings should be in 12-point type.

\subsection{Headings: second level}

Second-level headings should be in 10-point type.

\subsubsection{Headings: third level}

Third-level headings should be in 10-point type.

\paragraph{Paragraphs}

There is also a \verb+\paragraph+ command available, which sets the
heading in bold, flush left, and inline with the text, with the
heading followed by 1\,em of space.

\section{Citations, figures, tables, references}
\label{others}

These instructions apply to everyone.

\subsection{Citations within the text}

The \verb+natbib+ package will be loaded for you by default.
Citations may be author/year or numeric, as long as you maintain
internal consistency.  As to the format of the references themselves,
any style is acceptable as long as it is used consistently.

The documentation for \verb+natbib+ may be found at
\begin{center}
  \url{http://mirrors.ctan.org/macros/latex/contrib/natbib/natnotes.pdf}
\end{center}
Of note is the command \verb+\citet+, which produces citations
appropriate for use in inline text.  For example,
\begin{verbatim}
   \citet{hasselmo} investigated\dots
\end{verbatim}
produces
\begin{quote}
  Hasselmo, et al.\ (1995) investigated\dots
\end{quote}

If you wish to load the \verb+natbib+ package with options, you may
add the following before loading the \verb+nips_2016+ package:
\begin{verbatim}
   \PassOptionsToPackage{options}{natbib}
\end{verbatim}

If \verb+natbib+ clashes with another package you load, you can add
the optional argument \verb+nonatbib+ when loading the style file:
\begin{verbatim}
   \usepackage[nonatbib]{nips_2016}
\end{verbatim}

As submission is double blind, refer to your own published work in the
third person. That is, use ``In the previous work of Jones et
al.\ [4],'' not ``In our previous work [4].'' If you cite your other
papers that are not widely available (e.g., a journal paper under
review), use anonymous author names in the citation, e.g., an author
of the form ``A.\ Anonymous.''

\subsection{Footnotes}

Footnotes should be used sparingly.  If you do require a footnote,
indicate footnotes with a number\footnote{Sample of the first
  footnote.} in the text. Place the footnotes at the bottom of the
page on which they appear.  Precede the footnote with a horizontal
rule of 2~inches (12~picas).

Note that footnotes are properly typeset \emph{after} punctuation
marks.\footnote{As in this example.}

\subsection{Figures}

All artwork must be neat, clean, and legible. Lines should be dark
enough for purposes of reproduction. The figure number and caption
always appear after the figure. Place one line space before the figure
caption and one line space after the figure. The figure caption should
be lower case (except for first word and proper nouns); figures are
numbered consecutively.

You may use color figures.  However, it is best for the figure
captions and the paper body to be legible if the paper is printed in
either black/white or in color.
\begin{figure}[h]
  \centering
  \fbox{\rule[-.5cm]{0cm}{4cm} \rule[-.5cm]{4cm}{0cm}}
  \caption{Sample figure caption.}
\end{figure}

\subsection{Tables}

All tables must be centered, neat, clean and legible.  The table
number and title always appear before the table.  See
Table~\ref{sample-table}.

Place one line space before the table title, one line space after the
table title, and one line space after the table. The table title must
be lower case (except for first word and proper nouns); tables are
numbered consecutively.

Note that publication-quality tables \emph{do not contain vertical
  rules.} We strongly suggest the use of the \verb+booktabs+ package,
which allows for typesetting high-quality, professional tables:
\begin{center}
  \url{https://www.ctan.org/pkg/booktabs}
\end{center}
This package was used to typeset Table~\ref{sample-table}.

\begin{table}[t]
  \caption{Sample table title}
  \label{sample-table}
  \centering
  \begin{tabular}{lll}
    \toprule
    \multicolumn{2}{c}{Part}                   \\
    \cmidrule{1-2}
    Name     & Description     & Size ($\mu$m) \\
    \midrule
    Dendrite & Input terminal  & $\sim$100     \\
    Axon     & Output terminal & $\sim$10      \\
    Soma     & Cell body       & up to $10^6$  \\
    \bottomrule
  \end{tabular}
\end{table}

\section{Final instructions}

Do not change any aspects of the formatting parameters in the style
files.  In particular, do not modify the width or length of the
rectangle the text should fit into, and do not change font sizes
(except perhaps in the \textbf{References} section; see below). Please
note that pages should be numbered.

\section{Preparing PDF files}

Please prepare submission files with paper size ``US Letter,'' and
not, for example, ``A4.''

Fonts were the main cause of problems in the past years. Your PDF file
must only contain Type 1 or Embedded TrueType fonts. Here are a few
instructions to achieve this.

\begin{itemize}

\item You should directly generate PDF files using \verb+pdflatex+.

\item You can check which fonts a PDF files uses.  In Acrobat Reader,
  select the menu Files$>$Document Properties$>$Fonts and select Show
  All Fonts. You can also use the program \verb+pdffonts+ which comes
  with \verb+xpdf+ and is available out-of-the-box on most Linux
  machines.

\item The IEEE has recommendations for generating PDF files whose
  fonts are also acceptable for NIPS. Please see
  \url{http://www.emfield.org/icuwb2010/downloads/IEEE-PDF-SpecV32.pdf}

\item \verb+xfig+ "patterned" shapes are implemented with bitmap
  fonts.  Use "solid" shapes instead.

\item The \verb+\bbold+ package almost always uses bitmap fonts.  You
  should use the equivalent AMS Fonts:
\begin{verbatim}
   \usepackage{amsfonts}
\end{verbatim}
followed by, e.g., \verb+\mathbb{R}+, \verb+\mathbb{N}+, or
\verb+\mathbb{C}+ for $\mathbb{R}$, $\mathbb{N}$ or $\mathbb{C}$.  You
can also use the following workaround for reals, natural and complex:
\begin{verbatim}
   \newcommand{\RR}{I\!\!R} %real numbers
   \newcommand{\Nat}{I\!\!N} %natural numbers
   \newcommand{\CC}{I\!\!\!\!C} %complex numbers
\end{verbatim}
Note that \verb+amsfonts+ is automatically loaded by the
\verb+amssymb+ package.

\end{itemize}

If your file contains type 3 fonts or non embedded TrueType fonts, we
will ask you to fix it.

\subsection{Margins in \LaTeX{}}

Most of the margin problems come from figures positioned by hand using
\verb+\special+ or other commands. We suggest using the command
\verb+\includegraphics+ from the \verb+graphicx+ package. Always
specify the figure width as a multiple of the line width as in the
example below:
\begin{verbatim}
   \usepackage[pdftex]{graphicx} ...
   \includegraphics[width=0.8\linewidth]{myfile.pdf}
\end{verbatim}
See Section 4.4 in the graphics bundle documentation
(\url{http://mirrors.ctan.org/macros/latex/required/graphics/grfguide.pdf})

A number of width problems arise when \LaTeX{} cannot properly
hyphenate a line. Please give LaTeX hyphenation hints using the
\verb+\-+ command when necessary.

\subsubsection*{Acknowledgments}

Use unnumbered third level headings for the acknowledgments. All
acknowledgments go at the end of the paper. Do not include
acknowledgments in the anonymized submission, only in the final paper.

\section*{References}

References follow the acknowledgments. Use unnumbered first-level
heading for the references. Any choice of citation style is acceptable
as long as you are consistent. It is permissible to reduce the font
size to \verb+small+ (9 point) when listing the references. {\bf
  Remember that you can use a ninth page as long as it contains
  \emph{only} cited references.}
\medskip

\small

[1] Alexander, J.A.\ \& Mozer, M.C.\ (1995) Template-based algorithms
for connectionist rule extraction. In G.\ Tesauro, D.S.\ Touretzky and
T.K.\ Leen (eds.), {\it Advances in Neural Information Processing
  Systems 7}, pp.\ 609--616. Cambridge, MA: MIT Press.

[2] Bower, J.M.\ \& Beeman, D.\ (1995) {\it The Book of GENESIS:
  Exploring Realistic Neural Models with the GEneral NEural SImulation
  System.}  New York: TELOS/Springer--Verlag.

[3] Hasselmo, M.E., Schnell, E.\ \& Barkai, E.\ (1995) Dynamics of
learning and recall at excitatory recurrent synapses and cholinergic
modulation in rat hippocampal region CA3. {\it Journal of
  Neuroscience} {\bf 15}(7):5249-5262.

\end{document}

### 2016-10-12 paper.tex
Start writing paper

@@
 
-\usepackage{nips_2016}
+%\usepackage{nips_2016}
 
 % to compile a camera-ready version, add the [final] option, e.g.:
-% \usepackage[final]{nips_2016}
+\usepackage[final]{nips_2016}
 
@@
 
-\title{Formatting instructions for NIPS 2016}
+\title{Temporal Activity Detection in Untrimmed Videos with RNN}
 
@@
 \author{
-  David S.~Hippocampus\thanks{Use footnote for providing further
-    information about author (webpage, alternative
-    address)---\emph{not} for acknowledging funding agencies.} \\
-  Department of Computer Science\\
-  Cranberry-Lemon University\\
-  Pittsburgh, PA 15213 \\
-  \texttt{hippo@cs.cranberry-lemon.edu} \\
-  %% examples of more authors
-  %% \And
-  %% Coauthor \\
-  %% Affiliation \\
-  %% Address \\
-  %% \texttt{email} \\
-  %% \AND
-  %% Coauthor \\
-  %% Affiliation \\
-  %% Address \\
-  %% \texttt{email} \\
-  %% \And
-  %% Coauthor \\
-  %% Affiliation \\
-  %% Address \\
-  %% \texttt{email} \\
-  %% \And
-  %% Coauthor \\
-  %% Affiliation \\
-  %% Address \\
-  %% \texttt{email} \\
+    Alberto Montes \\
+    Polytechnic University of Catalonia \\
+    Barcelona, Catalonia/Spain \\
+    \texttt{al.montes.gomez@gmail.com} \\
+    \And
+    Amaia Salvador \\
+    Image Processing Group \\
+    Polytechnic University of Catalonia \\
+    Barcelona, Catalonia/Spain \\
+    \texttt{amaia.salvador@upc.edu} \\
+    \And
+    Xavi Giro-i-Nieto \\
+    Image Processing Group \\
+    Polytechnic University of Catalonia \\
+    Barcelona, Catalonia/Spain \\
+    \texttt{xavier.giro@upc.edu} \\
 }
@@
 \begin{abstract}
-  The abstract paragraph should be indented \nicefrac{1}{2}~inch
-  (3~picas) on both the left- and right-hand margins. Use 10~point
-  type, with a vertical spacing (leading) of 11~points.  The word
-  \textbf{Abstract} must be centered, bold, and in point size 12. Two
-  line spaces precede the abstract. The abstract must be limited to
-  one paragraph.
+    In the later years the applications of Deep Learning techniques have moved from images to videos due to the increase of computational resources available.
+In this field and in the classification task
 \end{abstract}

### 2016-10-13 paper.tex
Update on Overleaf.

@@
 % if you need to pass options to natbib, use, e.g.:
-% \PassOptionsToPackage{numbers, compress}{natbib}
+\PassOptionsToPackage{numbers, compress}{natbib}
 % before loading nips_2016
@@
 \begin{abstract}
+
     In the later years the applications of Deep Learning techniques have moved from images to videos due to the increase of computational resources available.
-In this field and in the classification task
+In this work, we propose a simple pipeline to classify and temporally localize activities on videos.
+The framework consist on a first stage to extract features from video segments using a 3D CNN and then a RNN which will predict a classification for each segment of the video.
+Some post-processing was applied at the output to be able to temporally localize activities on each video.
+
 \end{abstract}
 
-\section{Submission of papers to NIPS 2016}
+\section{Introduction}
 
-\textbf{There is a new style file for papers submitted in 2016!}
+Recognizing activities in videos has become a hot topic over the last years due to the continuous increase of video cameras devices and online repositories. 
+This large amount of data requires an automatic indexing to be accessed after capture.
+The recent advances in video coding, storage and computational resources have boosted research in the field towards new and more efficient solutions for organizing and retrieving video content.
 
-NIPS requires electronic submissions.  The electronic submission site
-is
-\begin{center}
-  \url{https://cmt.research.microsoft.com/NIPS2016/}
-\end{center}
+Impressive progress has been reported in the recent literature for video classification %% cites
+Recently it was starting facing the challenge to detect activities in untrimmed videos and this motivate another challenge topic: temporal localization of activities in videos.
+This task present a lot of real applications such as automatic trimmed of videos to keep the most interesting part.
+The possibilities are endless.
 
-Please read carefully the instructions below and follow them
-faithfully.
+\section{Related Work}
 
-\subsection{Style}
-
-Papers to be submitted to NIPS 2016 must be prepared according to the
-instructions presented here. Papers may only be up to eight pages
-long, including figures. Since 2009 an additional ninth page
-\emph{containing only acknowledgments and/or cited references} is
-allowed. Papers that exceed nine pages will not be reviewed, or in any
-other way considered for presentation at the conference.
-
-The margins in 2016 are the same as since 2007, which allow for
-$\sim$$15\%$ more words in the paper compared to earlier years.
-
-Authors are required to use the NIPS \LaTeX{} style files obtainable
-at the NIPS website as indicated below. Please make sure you use the
-current files and not previous versions. Tweaking the style files may
-be grounds for rejection.
-
-\subsection{Retrieval of style files}
-
-The style files for NIPS and other conference information are
-available on the World Wide Web at
-\begin{center}
-  \url{http://www.nips.cc/}
-\end{center}
-The file \verb+nips_2016.pdf+ contains these instructions and
-illustrates the various formatting requirements your NIPS paper must
-satisfy.
-
-The only supported style file for NIPS 2016 is \verb+nips_2016.sty+,
-rewritten for \LaTeXe{}.  \textbf{Previous style files for \LaTeX{}
-  2.09, Microsoft Word, and RTF are no longer supported!}
-
-The new \LaTeX{} style file contains two optional arguments:
-\verb+final+, which creates a camera-ready copy, and \verb+nonatbib+,
-which will not load the \verb+natbib+ package for you in case of
-package clash.
-
-At submission time, please omit the \verb+final+ option. This will
-anonymize your submission and add line numbers to aid review.  Please
-do \emph{not} refer to these line numbers in your paper as they will
-be removed during generation of camera-ready copies.
-
-The file \verb+nips_2016.tex+ may be used as a ``shell'' for writing
-your paper. All you have to do is replace the author, title, abstract,
-and text of the paper with your own.
-
-The formatting instructions contained in these style files are
-summarized in Sections \ref{gen_inst}, \ref{headings}, and
-\ref{others} below.
-
-\section{General formatting instructions}
-\label{gen_inst}
-
-The text must be confined within a rectangle 5.5~inches (33~picas)
-wide and 9~inches (54~picas) long. The left margin is 1.5~inch
-(9~picas).  Use 10~point type with a vertical spacing (leading) of
-11~points.  Times New Roman is the preferred typeface throughout, and
-will be selected for you by default.  Paragraphs are separated by
-\nicefrac{1}{2}~line space (5.5 points), with no indentation.
-
-The paper title should be 17~point, initial caps/lower case, bold,
-centered between two horizontal rules. The top rule should be 4~points
-thick and the bottom rule should be 1~point thick. Allow
-\nicefrac{1}{4}~inch space above and below the title to rules. All
-pages should start at 1~inch (6~picas) from the top of the page.
-
-For the final version, authors' names are set in boldface, and each
-name is centered above the corresponding address. The lead author's
-name is to be listed first (left-most), and the co-authors' names (if
-different address) are set to follow. If there is only one co-author,
-list both author and co-author side by side.
-
-Please pay special attention to the instructions in Section \ref{others}
-regarding figures, tables, acknowledgments, and references.
-
-\section{Headings: first level}
-\label{headings}
-
-All headings should be lower case (except for first word and proper
-nouns), flush left, and bold.
-
-First-level headings should be in 12-point type.
-
-\subsection{Headings: second level}
-
-Second-level headings should be in 10-point type.
-
-\subsubsection{Headings: third level}
-
-Third-level headings should be in 10-point type.
-
-\paragraph{Paragraphs}
-
-There is also a \verb+\paragraph+ command available, which sets the
-heading in bold, flush left, and inline with the text, with the
-heading followed by 1\,em of space.
-
-\section{Citations, figures, tables, references}
-\label{others}
-
-These instructions apply to everyone.
-
-\subsection{Citations within the text}
-
-The \verb+natbib+ package will be loaded for you by default.
-Citations may be author/year or numeric, as long as you maintain
-internal consistency.  As to the format of the references themselves,
-any style is acceptable as long as it is used consistently.
-
-The documentation for \verb+natbib+ may be found at
-\begin{center}
-  \url{http://mirrors.ctan.org/macros/latex/contrib/natbib/natnotes.pdf}
-\end{center}
-Of note is the command \verb+\citet+, which produces citations
-appropriate for use in inline text.  For example,
-\begin{verbatim}
-   \citet{hasselmo} investigated\dots
-\end{verbatim}
-produces
-\begin{quote}
-  Hasselmo, et al.\ (1995) investigated\dots
-\end{quote}
-
-If you wish to load the \verb+natbib+ package with options, you may
-add the following before loading the \verb+nips_2016+ package:
-\begin{verbatim}
-   \PassOptionsToPackage{options}{natbib}
-\end{verbatim}
-
-If \verb+natbib+ clashes with another package you load, you can add
-the optional argument \verb+nonatbib+ when loading the style file:
-\begin{verbatim}
-   \usepackage[nonatbib]{nips_2016}
-\end{verbatim}
-
-As submission is double blind, refer to your own published work in the
-third person. That is, use ``In the previous work of Jones et
-al.\ [4],'' not ``In our previous work [4].'' If you cite your other
-papers that are not widely available (e.g., a journal paper under
-review), use anonymous author names in the citation, e.g., an author
-of the form ``A.\ Anonymous.''
-
-\subsection{Footnotes}
-
-Footnotes should be used sparingly.  If you do require a footnote,
-indicate footnotes with a number\footnote{Sample of the first
-  footnote.} in the text. Place the footnotes at the bottom of the
-page on which they appear.  Precede the footnote with a horizontal
-rule of 2~inches (12~picas).
-
-Note that footnotes are properly typeset \emph{after} punctuation
-marks.\footnote{As in this example.}
-
-\subsection{Figures}
-
-All artwork must be neat, clean, and legible. Lines should be dark
-enough for purposes of reproduction. The figure number and caption
-always appear after the figure. Place one line space before the figure
-caption and one line space after the figure. The figure caption should
-be lower case (except for first word and proper nouns); figures are
-numbered consecutively.
-
-You may use color figures.  However, it is best for the figure
-captions and the paper body to be legible if the paper is printed in
-either black/white or in color.
-\begin{figure}[h]
-  \centering
-  \fbox{\rule[-.5cm]{0cm}{4cm} \rule[-.5cm]{4cm}{0cm}}
-  \caption{Sample figure caption.}
-\end{figure}
-
-\subsection{Tables}
-
-All tables must be centered, neat, clean and legible.  The table
-number and title always appear before the table.  See
-Table~\ref{sample-table}.
-
-Place one line space before the table title, one line space after the
-table title, and one line space after the table. The table title must
-be lower case (except for first word and proper nouns); tables are
-numbered consecutively.
-
-Note that publication-quality tables \emph{do not contain vertical
-  rules.} We strongly suggest the use of the \verb+booktabs+ package,
-which allows for typesetting high-quality, professional tables:
-\begin{center}
-  \url{https://www.ctan.org/pkg/booktabs}
-\end{center}
-This package was used to typeset Table~\ref{sample-table}.
-
-\begin{table}[t]
-  \caption{Sample table title}
-  \label{sample-table}
-  \centering
-  \begin{tabular}{lll}
-    \toprule
-    \multicolumn{2}{c}{Part}                   \\
-    \cmidrule{1-2}
-    Name     & Description     & Size ($\mu$m) \\
-    \midrule
-    Dendrite & Input terminal  & $\sim$100     \\
-    Axon     & Output terminal & $\sim$10      \\
-    Soma     & Cell body       & up to $10^6$  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-\section{Final instructions}
-
-Do not change any aspects of the formatting parameters in the style
-files.  In particular, do not modify the width or length of the
-rectangle the text should fit into, and do not change font sizes
-(except perhaps in the \textbf{References} section; see below). Please
-note that pages should be numbered.
-
-\section{Preparing PDF files}
-
-Please prepare submission files with paper size ``US Letter,'' and
-not, for example, ``A4.''
-
-Fonts were the main cause of problems in the past years. Your PDF file
-must only contain Type 1 or Embedded TrueType fonts. Here are a few
-instructions to achieve this.
-
-\begin{itemize}
-
-\item You should directly generate PDF files using \verb+pdflatex+.
-
-\item You can check which fonts a PDF files uses.  In Acrobat Reader,
-  select the menu Files$>$Document Properties$>$Fonts and select Show
-  All Fonts. You can also use the program \verb+pdffonts+ which comes
-  with \verb+xpdf+ and is available out-of-the-box on most Linux
-  machines.
-
-\item The IEEE has recommendations for generating PDF files whose
-  fonts are also acceptable for NIPS. Please see
-  \url{http://www.emfield.org/icuwb2010/downloads/IEEE-PDF-SpecV32.pdf}
-
-\item \verb+xfig+ "patterned" shapes are implemented with bitmap
-  fonts.  Use "solid" shapes instead.
-
-\item The \verb+\bbold+ package almost always uses bitmap fonts.  You
-  should use the equivalent AMS Fonts:
-\begin{verbatim}
-   \usepackage{amsfonts}
-\end{verbatim}
-followed by, e.g., \verb+\mathbb{R}+, \verb+\mathbb{N}+, or
-\verb+\mathbb{C}+ for $\mathbb{R}$, $\mathbb{N}$ or $\mathbb{C}$.  You
-can also use the following workaround for reals, natural and complex:
-\begin{verbatim}
-   \newcommand{\RR}{I\!\!R} %real numbers
-   \newcommand{\Nat}{I\!\!N} %natural numbers
-   \newcommand{\CC}{I\!\!\!\!C} %complex numbers
-\end{verbatim}
-Note that \verb+amsfonts+ is automatically loaded by the
-\verb+amssymb+ package.
-
-\end{itemize}
-
-If your file contains type 3 fonts or non embedded TrueType fonts, we
-will ask you to fix it.
-
-\subsection{Margins in \LaTeX{}}
-
-Most of the margin problems come from figures positioned by hand using
-\verb+\special+ or other commands. We suggest using the command
-\verb+\includegraphics+ from the \verb+graphicx+ package. Always
-specify the figure width as a multiple of the line width as in the
-example below:
-\begin{verbatim}
-   \usepackage[pdftex]{graphicx} ...
-   \includegraphics[width=0.8\linewidth]{myfile.pdf}
-\end{verbatim}
-See Section 4.4 in the graphics bundle documentation
-(\url{http://mirrors.ctan.org/macros/latex/required/graphics/grfguide.pdf})
-
-A number of width problems arise when \LaTeX{} cannot properly
-hyphenate a line. Please give LaTeX hyphenation hints using the
-\verb+\-+ command when necessary.
-
-\subsubsection*{Acknowledgments}
-
-Use unnumbered third level headings for the acknowledgments. All
-acknowledgments go at the end of the paper. Do not include
-acknowledgments in the anonymized submission, only in the final paper.
+The activity classification and temporal location tasks have been faced lately in Challenges such as the THUMOS~\cite{THUMOS15} and UCF101~\cite{UCF101}.
 
 \section*{References}
-
-References follow the acknowledgments. Use unnumbered first-level
-heading for the references. Any choice of citation style is acceptable
-as long as you are consistent. It is permissible to reduce the font
-size to \verb+small+ (9 point) when listing the references. {\bf
-  Remember that you can use a ninth page as long as it contains
-  \emph{only} cited references.}
-\medskip
-
-\small
-
-[1] Alexander, J.A.\ \& Mozer, M.C.\ (1995) Template-based algorithms
-for connectionist rule extraction. In G.\ Tesauro, D.S.\ Touretzky and
-T.K.\ Leen (eds.), {\it Advances in Neural Information Processing
-  Systems 7}, pp.\ 609--616. Cambridge, MA: MIT Press.
-
-[2] Bower, J.M.\ \& Beeman, D.\ (1995) {\it The Book of GENESIS:
-  Exploring Realistic Neural Models with the GEneral NEural SImulation
-  System.}  New York: TELOS/Springer--Verlag.
-
-[3] Hasselmo, M.E., Schnell, E.\ \& Barkai, E.\ (1995) Dynamics of
-learning and recall at excitatory recurrent synapses and cholinergic
-modulation in rat hippocampal region CA3. {\it Journal of
-  Neuroscience} {\bf 15}(7):5249-5262.
+{\small
+\bibliographystyle{plainnat}
+\bibliography{references}
+}
 

### 2016-10-14 paper.tex
Keep going with the paper

@@
 \usepackage{microtype}      % microtypography
+\usepackage{amsmath}        % equations
 
@@
 Impressive progress has been reported in the recent literature for video classification %% cites
-Recently it was starting facing the challenge to detect activities in untrimmed videos and this motivate another challenge topic: temporal localization of activities in videos.
+Recently it was starting facing the challenge to detect activities in untrimmed videos and this motivate another challenging topic: temporal localization of activities in videos.
 This task present a lot of real applications such as automatic trimmed of videos to keep the most interesting part.
-The possibilities are endless.
+We wanted to face this challenge and that is why we propose a simple pipeline which can be able to perform in both tasks.
+Our proposal consist in a Convolutional Neural Network to exploit spatial and short temporal correlations and then a Recurrent Neural Network which exploits long temporal correlations.
 
-\section{Related Work}
+\section{Related work}
 
-The activity classification and temporal location tasks have been faced lately in Challenges such as the THUMOS~\cite{THUMOS15} and UCF101~\cite{UCF101}.
+The activity classification and temporal localization tasks have been proposed with datasets such as Sports1M~\cite{KarpathyCVPR14}, THUMOS~\cite{THUMOS15} or ActivityNet~\cite{caba2015activitynet} published in the recents years.
+Many frameworks have been proposed to solve this tasks.
+Most of them use a Convolutional Neural Network to exploit the spatial correlations at each frame of the video such as in~\cite{gkioxari2015contextual,yeung2015end,ballas2015delving}.
+But as videos also present temporal correlations, the combination of the frames information and the computed optical flow has been used~\cite{wang2015towards} in a CNN to improve the results.
 
-\section*{References}
+Recently, was proposed by~\cite{tran2014learning} a new CNN which use 3D convolutions instead of 2D and apply them into chunks of video frames to classify videos.
+This 3D convolutions exploits short temporal correlations between frames and have demonstrated to work well in classifying videos~\cite{tran2014learning,tran2015deep}.
+In addition to this solutions, it has been proposed~\cite{shoutemporal} a multi-stage 3D CNN in order to predict temporal localization in videos in addition to the classification.
+
+Finally, in relation with the temporal localization of activities, it has been proposed the use of Recurrent Neural Networks.
+This networks exploit long and short temporal correlations and this caracteristic make them very suitable for video applications.
+It has been proposed the usage of RNN after CNN~\cite{yao2015describing} and also using reinforcement learning~\cite{yeung2015every} to temporally localize activities in videos.
+
+\section{Details of the proposed network}
+
+\paragraph{3D Convolutional Neural Network.}
+First, each video is split in clips of 16 frames and then each clip is resized ot 171 (width) $\times$ 128 (heigh) pixels.
+This is the input size of the C3 ConvNet proposed in~\cite{tran2014learning}.
+This network conducts 3D convolutions/pooling which operates in spatial and temporal dimensions simultaneously, and therefore can capture both appearance and motion.
+All 3D pooling layers use a 2$\times$2 max pooling with stride 2 in spatial dimensions, the same kernel size as in the temporal dimension except the first pooling layer (\texttt{pool1}) which has kernel size 1 and stride 1.
+All 3D convolutional filters have kernel size 3 and stride 1 in all dimensions.
+
+The network architecture used is the same as in the original paper except that it has been decided to work on the next stage with the values obtained at the \texttt{fc6} layer as feature vector for each 16-frame clip.
+The specifications of the network layers as well as the number of kernels by layer is the following one: \texttt{conv1(64) - pool1 - conv2a(128) - pool2 - conv3a(256) - conv3b(256) - pool3 - conv4a(512) - conv4b(512) - pool4 - conv5a(512) - conv5b(512) - pool(5) - fc6(4096)}.
+
+This 3D ConvNet was trained on Sports1M training subset~\cite{tran2014learning} and the resulting network weights were used to extract feature vectors for our network.
+
+\paragraph{Recurrent Neural Network.}
+The next step is to use a RNN to exploit long temporal correlations between video clips. Our proposal consist on using LSTM cells thanks to its long term memory.
+The network has been design to given a sequence of features vectors, return a sequence of classes corresponding the probability of each clip belong to one of the classes of the dataset.
+To avoid overfitting it has been dropout before and after the recurrent layers with probabily $p = .5$.
+Also the output correspond to a Softmax with the same number of outputs as number of classes $K$ plus the background class.
+
+The recurrent network have the following architecture: \texttt{input(4096) - dropout(.5) - N $\times$ lstm(c) - dropout(.5) - softmax(K+1)}.
+Different configurations of the number of LSTM layers $M$ and the number of cells $c$ has been tested in order to find the one with best performance.
+
+\paragraph{Training procedure.}
+From our proposed network, only the second stage was trained due to computational restrictions and the fact that the first stage was already trained with a video dataset.
+To train the recurrent network with the extracted features, was found that most of the videos had a clip length larger than a valid timestep at training, so a stateful approach was used at training where the memory was not reset between batches and at the same batch position was placed the continuation of the features of the previous seen video.
+
+In addition to this, it was also required to weight the loss function due to the imbalance of the output classes where the background instances present a higher frequence of appearance.
+The loss used at training was the categorical cross entropy and the weigthed for is as follows, where $q$ is the predicted probability distribution and $p$ the ground truth probability distribution:
+
+\begin{equation}
+    H(p,q) = - \sum_x \alpha(x) p(x) \log (q(x)), \text{ where } \alpha(x) =
+    \begin{cases}
+        \rho, & x = \text{background instance}\\
+        1,    & \text{otherwise}
+    \end{cases}
+\end{equation}
+
+\paragraph{Post-Processing.}
+The prediction of the recurrent network consist on a sequence of probabilities corresponding to each of the classes at the dataset.
+The goal of this network is to be able to classify globaly the video given at the input and also the temporal localization of the activity previously classified.
+To achieve so, some post-processing is required.
+To classify the video, the mean is computed along all the sequence predicted as follows:
+
+\begin{equation}
+	p_{video}(x) = \frac{1}{T_{video}} \sum_i^{video} p_i(x), \text{where } x \in \{ \text{Dataset Activities}\}
+\end{equation}
+
+where $T_{video}$ is the length of the video in number of 16-frames clips.
+From the obtain probability of the video to belong to each of the classes, the class with the maximum probability is chosen for the classification task.
+
+On the other hand, to obtain the temporal localization of the class previously predicted, first is passed the sequence of probabilities in a mean filter of $k$ samples to smooth the values along time space as in Equation~\ref{eq:smooth}.
+Then the probability of activity is computed at each step of the sequence such as in Equation~\ref{eq:activity_probability}.
+Finally a threshold $\gamma$ is set and all the clips with an activity probability higher than $\gamma$ are considered for detection.
+
+\begin{equation}
+	\tilde{p}_i(x) = \frac{1}{2k} \sum_{j=i-k}^{i+k} p_i(x)
+    \label{eq:smooth}
+\end{equation}
+
+\begin{equation}
+    \label{eq:activity_probability}
+	\tilde{p}^a_i = \sum_{x=1}^{200}\tilde{p}_i(x), \text{where } x = \begin{cases}
+        0, & \text{background class} \\
+        i, & 1 \leq i \leq 200 \text{ activity classes}
+    \end{cases}
+\end{equation}
+
+\section{Experiments}
+
+\subsection{Dataset}
+
+Talk about ActivityNet dataset
+
+\subsection{Network configurations}
+
+Talk about different values of N and c
+
+\subsection{Post-processing parameters}
+
+talk about different experiments with values of $\gamma$ and k
+
+\section{Conclusion}
+
+Explain conclusion
+
+\section*{}
 {\small

### 2016-10-14 paper.tex
Add note
Update on Overleaf.

@@
     \And
-    Xavi Giro-i-Nieto \\
+    Xavier Giro-i-Nieto \\
     Image Processing Group \\
@@
 
-Explain conclusion
+Explain conclusions. Give at the footnote to the repo where all the code is available.
 

### 2016-10-14 paper.tex
Update on Overleaf.

--- 2016-10-13 paper.tex
@@
 \usepackage{microtype}      % microtypography
+\usepackage{amsmath}        % equations
 
-\title{Temporal Activity Detection in Untrimmed Videos with RNN}
+\title{Temporal Activity Detection in Untrimmed Videos with Recurrent Neural Networks}
 
@@
     Alberto Montes \\
-    Polytechnic University of Catalonia \\
-    Barcelona, Catalonia/Spain \\
+    Universitat Politècnica de Catalunya \\
+    Barcelona, Spain \\
     \texttt{al.montes.gomez@gmail.com} \\
@@
     Image Processing Group \\
-    Polytechnic University of Catalonia \\
-    Barcelona, Catalonia/Spain \\
+    Universitat Politècnica de Catalunya \\
+    Barcelona, Spain \\
     \texttt{amaia.salvador@upc.edu} \\
     \And
-    Xavi Giro-i-Nieto \\
+    Xavier Giro-i-Nieto \\
     Image Processing Group \\
-    Polytechnic University of Catalonia \\
-    Barcelona, Catalonia/Spain \\
+    Universitat Politècnica de Catalunya \\
+    Barcelona, Spain \\
     \texttt{xavier.giro@upc.edu} \\
@@
 
-    In the later years the applications of Deep Learning techniques have moved from images to videos due to the increase of computational resources available.
-In this work, we propose a simple pipeline to classify and temporally localize activities on videos.
-The framework consist on a first stage to extract features from video segments using a 3D CNN and then a RNN which will predict a classification for each segment of the video.
-Some post-processing was applied at the output to be able to temporally localize activities on each video.
+% AMAIA: La primera frase de l'abstract potser no cal, ja que és massa introductoria. L'he comentat i modificat l'abstract
 
+    %In the later years the applications of deep learning techniques have moved from images to videos due to the increase of computational resources available.
+
+    This work proposes a simple pipeline to classify and temporally localize activities in untrimmed videos.
+Our system uses features from a 3D Convolutional Neural Network (3D-CNN) as input to train a a recurrent neural network (RNN) that learns to classify each segment of the video.
+After training, we post-process the output of the RNN to be able to both assign a single activity label to each video and temporally localize when that activity happens within the input video.
+We find that our system can achieve competitive results in both tasks with a simple architecture composed.
+We evaluate our method in the ActivityNet Challenge 2016, achieving a 0.00 mAP and a 0.00 mAP in the classification and detection tasks, respectively.
+Our code and models can be found at: \url{ https://github.com/imatge-upc/activitynet-2016-cvprw}
+
+%AMAIA: s'han d'afegir els valors de mAP (o la metrica que sigui)
 \end{abstract}
@@
 
-Impressive progress has been reported in the recent literature for video classification %% cites
-Recently it was starting facing the challenge to detect activities in untrimmed videos and this motivate another challenge topic: temporal localization of activities in videos.
-This task present a lot of real applications such as automatic trimmed of videos to keep the most interesting part.
-The possibilities are endless.
+Impressive progress has been reported in the recent literature for video classification \cite{}, which requires to assign a label for the input video.
+While this task is already challenging, it typically requires videos to be trimmed beforehand (i.e.
+the category is present in the entire video).
+However, a video classification system should be able to recognize activities in untrimmed videos, and find the temporal segments in which they appear.
+This second challenge has been recently proposed in the ActivityNet Challenge 2016 \cite{}, in which participants are asked to both provide a single activity for each video, as well as the temporal segment where the activity happened in the video.
+% AMAIA: Amb això et refereixes que la tasca de detecció temporal es nova d'Activitynet?
+Ho he modificat una mica...
+No queda massa clar...
+Si és així, jo directament mencionaria la challenge i la citaria.
+In order to face both these challenges at the same time, we propose a simple pipeline composed of a 3D-CNN that exploits spatial and short temporal correlations followed by a recurrent neural network which exploits long temporal correlations.
 
-\section{Related Work}
+% AMAIA: Decidim si volem dir 'CNN' o 'ConvNet'. Ara ho he deixat tot amb CNN. Millor no barrejar
 
-The activity classification and temporal location tasks have been faced lately in Challenges such as the THUMOS~\cite{THUMOS15} and UCF101~\cite{UCF101}.
+\section{Related work}
 
-\section*{References}
+% AMAIA: El related work dels datasets me'l saltaria per guanyar espai. L'he comentat.
+
+%The activity classification and temporal localization tasks have been proposed with datasets such as Sports1M~\cite{KarpathyCVPR14}, THUMOS~\cite{THUMOS15} or ActivityNet~\cite{caba2015activitynet} published in the recents years.
+Many frameworks have been proposed to solve this tasks.
+Several works in the literature have used 2D-CNNs to exploit the spatial correlations between frames of a video by combining their outputs using different strategies~\cite{gkioxari2015contextual,yeung2015end,ballas2015delving}.
+Others have tried using the optical flow as an additional input to the 2D-CNN videos~\cite{wang2015towards}, which provides information of the temporal correlations.
+% AMAIA: Tot això s'ha de revisar...
+
+Later on, 3D-CNNs were proposed in ~\cite{tran2014learning}, which were able to exploit short temporal correlations between frames and have demonstrated to work remarkably well for video classification~\cite{tran2014learning,tran2015deep}.
+3D-CNNs have also been used for temporal detection in~\cite{shoutemporal}, where multi-stage 3D-CNN architecture is used to classify video segment proposals.
+
+For temporal activity detection, recent works have proposed the usage of Long Short-Term Memory units (LSTM) \cite{}.
+LSTMs are a type of RNNs that is able to better exploit long and short temporal correlations in sequences, which makes them suitable for video applications.
+LSTMs have been used alongside CNNs for video classification ~\cite{yao2015describing} and activity localization in videos~\cite{yeung2015every}.
+
+% AMAIA: Aquí falta una frase que digui què fem diferent nosaltres, en què ens assemblem a l'estat de l'art...
+
+\section{Proposed Architecture}
+% AMAIA: He tret això dels paràgrafs, ja que ocupen massa espai i no tenim tantes coses per explicar...
+
+% AMAIA: Ja sé que són 4 pàgines...però crec que estaria bé posar la figura de l'arquitectura no??
+Potser, per aprofitar l'espai, pots fer una figura doble (o triple), i en cada columna pots posar una cosa: e.g.
+1.
+Arquitectura (figura 1.1 de la teva memoria) 2.
+exemples visuals(que mostrin un frame del video, prediccio i groundtruth).
+La figura que també m'agrada és la 4.10 o 4.11 de la memòria (potser no cal posar-la sencera), on expliques diferents prediccions (a vegades la detecció està bé pero la classe global no, o al revés...).
+Jo crec que aquestes figures t'ajudaran a explicar els resultats i conclusions.
+https://imatge.upc.edu/web/sites/default/files/pub/xMontes.pdf
+
+% AMAIA: Pel tema de les figures, si veus que ocupa molt pots descartar-ne alguna... depen del que vulguis explicar a la secció d'experiments
+
+%\paragraph{3D-CNN.}
+We use the 3D-CNN model proposed in~\cite{tran2014learning} to extract features for all videos in the database.
+We split the videos in 16-frame clips and resize them to 171$\times$128 to fit the original model's desired input.
+Features from the second fully connected layer (fc6) are extracted for each video clip.
+
+% AMAIA: Els detalls de la xarxa no calen, ja que no l'hem dissenyat nosaltres. Els comento
+
+%This network conducts 3D convolutions/pooling which operates in spatial and temporal dimensions simultaneously, and therefore can capture both appearance and motion.
+%All 3D pooling layers use a 2$\times$2 max pooling with stride 2 in spatial dimensions, the same kernel size as in the temporal dimension except the first pooling layer (\texttt{pool1}) which has kernel size 1 and stride 1.
+All 3D convolutional filters have kernel size 3 and stride 1 in all dimensions.
+%The network architecture used is the same as in the original paper except that it has been decided to work on the next stage with the values obtained at the \texttt{fc6} layer as feature vector for each 16-frame clip.
+The specifications of the network layers as well as the number of kernels by layer is the following one: \texttt{conv1(64) - pool1 - conv2a(128) - pool2 - conv3a(256) - conv3b(256) - pool3 - conv4a(512) - conv4b(512) - pool4 - conv5a(512) - conv5b(512) - pool(5) - fc6(4096)}.
+
+%\paragraph{Recurrent Neural Network.}
+Next, we design a network that takes a sequence of 3D-CNN-f6 features from a video, and returns a sequence of class probabilities for each element in the sequence.
+We use LSTM layers, followed with dropout with $p = .5$ and a fully connected layer with a softmax activation.
+Figure \ref{} shows the proposed architecture.
+Different configurations of the number of LSTM layers $M$ and the number of cells $c$ have been tested and will be reviewed in the following sections.
+
+%The recurrent network have the following architecture: \texttt{input(4096) - dropout(.5) - N $\times$ lstm(c) - dropout(.5) - softmax(K+1)}.
+
+%\paragraph{Training.}
+%To train the recurrent network with the extracted features, was found that most of the videos had a clip length larger than a valid timestep at training, so a stateful approach was used at training where the memory was not reset between batches and at the same batch position was placed the continuation of the features of the previous seen video.
+
+% AMAIA: Això de stateful i tal no cal no?
+
+\section{Post-Processing}
+Given a video, the prediction of our model is sequence of class probabilities for each 16-frame video clip.
+From this output, we need to be able to predict the activity  and temporally localize it.
+We post-process the network's output to achieve that goal.
+First, to obtain the activity prediction for the whole video, we simply compute the mean over all video clips in the video.
+We then take the class with maximum predicted probability as the predicted class.
+
+%\begin{equation}
+%	p(x) = \frac{1}{T} \sum_i^{T} p_i(x)
+%\end{equation}
+
+%where $T$ is number of video clips of 16 frames in the video. 
+% AMAIA: No cal posar l'equació de la mitja...
+
+To obtain the temporal localization of the predicted activity, we first apply a mean filter of $k$ samples to the predicted sequence to smooth the values through time (see equation~\ref{eq:smooth}).
+Then, the probability of activity (vs no activity) is computed for all samples of the sequence, being the activity probability the sum of all activity probabilities, and the no activity probability, the one assigned to the background class.
+Finally, a threshold $\gamma$ is set and all clips with probability higher than $\gamma$ are considered as part of the detected temporal segment for the previously assigned activity.
+
+\begin{equation}
+	\tilde{p}_i(x) = \frac{1}{2k} \sum_{j=i-k}^{i+k} p_i(x)
+    \label{eq:smooth}
+\end{equation}
+
+% \begin{equation}
+%     \label{eq:activity_probability}
+% 	\tilde{p}^a_i = \sum_{x=1}^{N}\tilde{p}_i(x), \text{where } x = \begin{cases}
+%         0, & \text{background class} \\
+%         i, & 1 \leq i \leq N \text{ activity classes}
+%     \end{cases}
+% \end{equation}
+
+% AMAIA: Aquesta equació està be ??
+Vull dir, no cal posar where x = blabla..., és simplement la suma de les probabilitats de 1 a N no?
+De fet crec que tampoc cal posar-la...
+Ho he explicat al text.
+Potser podria quedar més clar...
+
+\section{Experiments}
+
+\subsection{Dataset}
+For all our experiments we use the dataset provided in the ActivityNet Challenge 2016 \cite{}.
+This dataset contains 640 hours of video and 64 million frames.
+The ActivityNet dataset is composed of untrimmed videos, providing temporal annotations for the given ground truth class labels.
+
+\subsection{Training}
+% AMAIA: He mogut la part de training a experiments
+We train the network described in Section \ref{} with the negative log likelihood loss, assigning a lower weight to background samples to deal with dataset imbalance( see equation \ref{eq:loss}).
+
+\begin{equation}
+    L(p,q) = - \sum_x \alpha(x) p(x) \log (q(x)), \text{ where } \alpha(x) =
+    \begin{cases}
+        \rho, & x = \text{background instance}\\
+        1,    & \text{otherwise}
+    \end{cases}
+    \label{eq:loss}
+\end{equation}
+
+where $q$ is the predicted probability distribution and $p$ the ground truth probability distribution. In our experiments, we set $\rho$ = X. 
+% What is the value of \rho ??
+
+% AMAIA: Aquí tambe hauries d'afegir el numero de iteracions (o epochs), learning rate, optimizer, batch size. Si el tens, el temps d'entrenament en la GPU que entrenessis.
+
+\subsection{Results}
+
+Talk about different values of N and c
+talk about different experiments with values of $\gamma$ and k
+
+% AMAIA: Crec que amb una secció on expliquis tots els experiments ja n'hi ha prou. Li he posat el nom de 'Results'
+
+% AMAIA: Si aqui vols parlar del bias towards sport categories, hauries d'afegir la figura que tens que ho demostra. 
+\section{Conclusion}
+
+Explain conclusions. Give at the footnote to the repo where all the code is available.
+
+% AMAIA: La url del repo ja l'he posat a l'abstract.
+
+\section*{}
 {\small

### 2016-10-15 paper.tex
Abstract reviewev by Xavi

@@
 \usepackage{amsmath}        % equations
+\usepackage{color}
 
@@
     This work proposes a simple pipeline to classify and temporally localize activities in untrimmed videos.
-Our system uses features from a 3D Convolutional Neural Network (3D-CNN) as input to train a a recurrent neural network (RNN) that learns to classify each segment of the video.
-After training, we post-process the output of the RNN to be able to both assign a single activity label to each video and temporally localize when that activity happens within the input video.
-We find that our system can achieve competitive results in both tasks with a simple architecture composed.
+Our system uses features from a 3D Convolutional Neural Network (3D-CNN) as input to train a a recurrent neural network (RNN) that learns to classify video clips of 16 frames.
+After clip prediction, we post-process the output of the RNN to assign a single activity label to each video, and determine the temporal boundaries of the activity within the video.
+We show how our system can achieve competitive results in both tasks with a simple architecture.
 We evaluate our method in the ActivityNet Challenge 2016, achieving a 0.00 mAP and a 0.00 mAP in the classification and detection tasks, respectively.
-Our code and models can be found at: \url{ https://github.com/imatge-upc/activitynet-2016-cvprw}
+Our code and models are publicly acailable at at: \url{ https://github.com/imatge-upc/activitynet-2016-cvprw}
 

### 2016-10-15 paper.tex
Update on Overleaf.

@@
 
-Recognizing activities in videos has become a hot topic over the last years due to the continuous increase of video cameras devices and online repositories.
+Recognizing activities in videos has become a hot topic over the last years due to the continuous increase of video capturing devices and online repositories.
 This large amount of data requires an automatic indexing to be accessed after capture.

### 2016-10-15 paper.tex
Finishing paper

@@
 \usepackage{color}
+\usepackage{graphicx}
+\usepackage{subcaption}
 
@@
 
-    %In the later years the applications of deep learning techniques have moved from images to videos due to the increase of computational resources available.
-
     This work proposes a simple pipeline to classify and temporally localize activities in untrimmed videos.
@@
 We show how our system can achieve competitive results in both tasks with a simple architecture.
-We evaluate our method in the ActivityNet Challenge 2016, achieving a 0.00 mAP and a 0.00 mAP in the classification and detection tasks, respectively.
-Our code and models are publicly acailable at at: \url{ https://github.com/imatge-upc/activitynet-2016-cvprw}
+We evaluate our method in the ActivityNet Challenge 2016, achieving a 0.5874 mAP and a 0.2237 mAP in the classification and detection tasks, respectively.
+Our code and models are publicly available at at: \url{https://github.com/imatge-upc/activitynet-2016-cvprw}
 
-%AMAIA: s'han d'afegir els valors de mAP (o la metrica que sigui)
+%AMAIA: s'han d'afegir els valors de mAP (o la metrica que sigui).
+%ALBERTO: FET
 \end{abstract}
@@
 
-Impressive progress has been reported in the recent literature for video classification \cite{}, which requires to assign a label for the input video.
+Impressive progress has been reported in the recent literature for video classification~\cite{tran2014learning,tran2015deep,wang2015towards,yao2015describing}, which requires to assign a label for the input video.
 While this task is already challenging, it typically requires videos to be trimmed beforehand (i.e.
@@
 However, a video classification system should be able to recognize activities in untrimmed videos, and find the temporal segments in which they appear.
-This second challenge has been recently proposed in the ActivityNet Challenge 2016 \cite{}, in which participants are asked to both provide a single activity for each video, as well as the temporal segment where the activity happened in the video.
+This second challenge has been recently proposed in the ActivityNet Challenge 2016~\cite{caba2015activitynet}, in which participants are asked to both provide a single activity for each video, as well as the temporal segment where the activity happened in the video.
 % AMAIA: Amb això et refereixes que la tasca de detecció temporal es nova d'Activitynet?
@@
 
-For temporal activity detection, recent works have proposed the usage of Long Short-Term Memory units (LSTM) \cite{}.
+For temporal activity detection, recent works have proposed the usage of Long Short-Term Memory units (LSTM)~\cite{hochreiter1997long}.
 LSTMs are a type of RNNs that is able to better exploit long and short temporal correlations in sequences, which makes them suitable for video applications.
-LSTMs have been used alongside CNNs for video classification ~\cite{yao2015describing} and activity localization in videos~\cite{yeung2015every}.
+LSTMs have been used alongside CNNs for video classification~\cite{yao2015describing} and activity localization in videos~\cite{yeung2015every}.
 
@@
 
-%\paragraph{3D-CNN.}
 We use the 3D-CNN model proposed in~\cite{tran2014learning} to extract features for all videos in the database.
@@
 
-%\paragraph{Recurrent Neural Network.}
+\subsection{Recurrent Neural Network}
+\label{sec:architecture}
 Next, we design a network that takes a sequence of 3D-CNN-f6 features from a video, and returns a sequence of class probabilities for each element in the sequence.
 We use LSTM layers, followed with dropout with $p = .5$ and a fully connected layer with a softmax activation.
-Figure \ref{} shows the proposed architecture.
-Different configurations of the number of LSTM layers $M$ and the number of cells $c$ have been tested and will be reviewed in the following sections.
+Figure~\ref{fig:global_pipeline} shows the proposed architecture.
+Different configurations of the number of LSTM layers and the number of cells have been tested and will be reviewed in the following sections.
+
+\begin{figure}[ht]
+\centering
+\includegraphics[width=.5\linewidth]{img/schematic_pipeline}
+\caption{Global architecture of the proposed pipeline.}
+\label{fig:global_pipeline}
+\end{figure}
 
@@
 
-\section{Post-Processing}
+\subsection{Post-Processing}
 Given a video, the prediction of our model is sequence of class probabilities for each 16-frame video clip.
@@
 \subsection{Dataset}
-For all our experiments we use the dataset provided in the ActivityNet Challenge 2016 \cite{}.
+For all our experiments we use the dataset provided in the ActivityNet Challenge 2016~\cite{caba2015activitynet}.
 This dataset contains 640 hours of video and 64 million frames.
 The ActivityNet dataset is composed of untrimmed videos, providing temporal annotations for the given ground truth class labels.
+The dataset is split in 50\% for training, 25\% for validation and 25\% for testing.
 
 \subsection{Training}
-% AMAIA: He mogut la part de training a experiments
-We train the network described in Section \ref{} with the negative log likelihood loss, assigning a lower weight to background samples to deal with dataset imbalance( see equation \ref{eq:loss}).
+We train the network described in Section~\ref{sec:architecture} with the negative log likelihood loss, assigning a lower weight to background samples to deal with dataset imbalance (see Equation~\ref{eq:loss}).
 
@@
 
-where $q$ is the predicted probability distribution and $p$ the ground truth probability distribution. In our experiments, we set $\rho$ = X. 
-% What is the value of \rho ??
+where $q$ is the predicted probability distribution and $p$ the ground truth probability distribution. In our experiments, we set $\rho$ = .3.
+
+The network was trained with a 256 batch size and 20 \textit{timesteps} as input sequence.
+The optimezer function used was the RMSprop~\cite{dauphin2015rmsprop} with a learning rate set to $10^{-5}$. In total the network was trained with 100 epochs.
 
 % AMAIA: Aquí tambe hauries d'afegir el numero de iteracions (o epochs), learning rate, optimizer, batch size. Si el tens, el temps d'entrenament en la GPU que entrenessis.
+% ALBERTO: FET
 
@@
 
-Talk about different values of N and c
-talk about different experiments with values of $\gamma$ and k
+The evaluation metric follow the metric used in ActivityNet Challenge to regard classification and temporal activity localization as retrieval probelm and evaluate the mAP.
+For temporal localization, a prediction is masrked correct only when it has the correct category and has IoU with ground truth instance larger than $0.5$.
 
+\begin{table}[h]
+    \parbox{.45\linewidth}{
+        \centering
+        \begin{tabular}{l|cc}
+        \textbf{Architecture} & \textbf{mAP} & \textbf{Hit@3} \\
+        \hline
+        3 x 1024-LSTM & 0.5635 & 0.7437 \\
+        2 x 512-LSTM & 0.5492 & 0.7364 \\
+        1 x 512-LSTM & \bf0.5938 & \bf0.7576 \\
+        \end{tabular}
+        \vspace{.5cm}
+        \caption{Results for classification task comparing different architectures.}
+        \label{table:classification_by_architecture}
+    }
+    \hfill
+    \parbox{.45\linewidth}{
+        \centering
+        \begin{tabular}{l|ccc}
+        \textbf{$\gamma$} & \textbf{$k=0$} & \textbf{$k=5$} & \textbf{$k=10$} \\
+        \hline
+        0.2 & 0.20732 & \bf0.22513 & 0.22136 \\
+        0.3 & 0.19854 & 0.22077 & 0.22100 \\
+        0.5 & 0.19035 & 0.21937 & 0.21302 \\
+        \end{tabular}
+        \vspace{.2cm}
+        \caption{mAP with an IOU threshold of $0.5$ comparing between values of $k$ and $\gamma$ on post-processing.}
+        \label{table:detection_postprocessing_comparison}
+    }
+\end{table}
+
+The first results are related with the network architecture.
+It has been tested with different number of layers and different number of cells having all the layers the same number of cells.
+The results can be found in Table~\ref{table:classification_by_architecture}.
+This results indicate that all the networks presented high learning capacity over the data ans it was obeseved a little over-fitting with the deeper architectures, obtainng the best results with a single layer of 512-LSTM cells.
+
+Once the architecture has been chosen to obtain the best performance in the classification task, some experiments with different values of $k$ and $\gamma$ for the post-processing were performed.
+At Table~\ref{table:detection_postprocessing_comparison} there is the results for the temporal activity localization task, where can be seen that the effect of a mean filter to smooth helps improving the localization.
+
+% \begin{table}[h]
+% \begin{center}
+% \begin{tabular}{|l|c|c|}
+% \hline
+% \textbf{Architecture} & \textbf{mAP} & \textbf{Hit@3} \\
+% \hline\hline
+% 3 x 1024-LSTM & 0.5635 & 0.7437 \\
+% 2 x 512-LSTM & 0.5492 & 0.7364 \\
+% 1 x 512-LSTM & \bf0.5938 & \bf0.7576 \\
+% \hline
+% \end{tabular}
+% \end{center}
+% \caption{Results for classification task comparing different deep architectures. All values with
+%          only video features on the validation dataset.}
+% \label{table:classification_by_architecture}
+% \end{table}
+%
+% \begin{table}[h]
+% \begin{center}
+% \begin{tabular}{|l|c|c|c|}
+% \hline
+% \textbf{$\gamma$} & \textbf{$k=0$} & \textbf{$k=5$} & \textbf{$k=10$} \\
+% \hline
+% \textbf{0.2} & 0.20732 & \bf0.22513 & 0.22136 \\
+% \textbf{0.3} & 0.19854 & 0.22077 & 0.22100 \\
+% \textbf{0.5} & 0.19035 & 0.21937 & 0.21302 \\
+% \hline
+% \end{tabular}
+% \end{center}
+% \caption{mAP with an IOU threshold of $0.5$ over validation dataset. Here there is a comparison
+% between values of $k$ and $\gamma$ on post processing.}
+% \label{table:detection_postprocessing_comparison}
+% \end{table}
+% \end{multicols}
+
+% \begin{figure}
+% \centering
+% \subfloat[][]{
+% \begin{table}[h]
+% \begin{center}
+% \begin{tabular}{|l|c|c|}
+% \hline
+% \textbf{Architecture} & \textbf{mAP} & \textbf{Hit@3} \\
+% \hline\hline
+% 3 x 1024-LSTM & 0.5635 & 0.7437 \\
+% 2 x 512-LSTM & 0.5492 & 0.7364 \\
+% 1 x 512-LSTM & \bf0.5938 & \bf0.7576 \\
+% \hline
+% \end{tabular}
+% \end{center}
+% \caption{Results for classification task comparing different deep architectures. All values with
+%          only video features on the validation dataset.}
+% \label{table:classification_by_architecture}
+% \end{table}
+% }
+% \qquad
+% \begin{table}[h]
+% \begin{center}
+% \begin{tabular}{|l|c|c|c|}
+% \hline
+% \textbf{$\gamma$} & \textbf{$k=0$} & \textbf{$k=5$} & \textbf{$k=10$} \\
+% \hline
+% \textbf{0.2} & 0.20732 & \bf0.22513 & 0.22136 \\
+% \textbf{0.3} & 0.19854 & 0.22077 & 0.22100 \\
+% \textbf{0.5} & 0.19035 & 0.21937 & 0.21302 \\
+% \hline
+% \end{tabular}
+% \end{center}
+% \caption{mAP with an IOU threshold of $0.5$ over validation dataset. Here there is a comparison
+% between values of $k$ and $\gamma$ on post processing.}
+% \label{table:detection_postprocessing_comparison}
+% \end{table}
+%
+% \end{figure}
+
+In the Figure~\ref{fig:example_results} is shown some examples of the temporal localization prediction for some instances of the dataset.
+It can be seen how the predictions are continuous and smooth and mostly overlaps with the ground truth instances.
+
+\begin{figure}[ht]
+\centering
+\includegraphics[width=1\linewidth]{img/activity_temporal_localization_8.png}
+\includegraphics[width=1\linewidth]{img/activity_temporal_localization_11.png}
+\includegraphics[width=1\linewidth]{img/activity_temporal_localization_20.png}
+\includegraphics[width=1\linewidth]{img/activity_temporal_localization_35.png}
+
+\caption{Global architecture of the proposed pipeline.}
+\label{fig:example_results}
+\end{figure}
 % AMAIA: Crec que amb una secció on expliquis tots els experiments ja n'hi ha prou. Li he posat el nom de 'Results'
@@
 % AMAIA: Si aqui vols parlar del bias towards sport categories, hauries d'afegir la figura que tens que ho demostra.
+% ALBERTO: crec que potser una segona figura no hi cab...posar-la a annexes potser???
 \section{Conclusion}
 
-Explain conclusions. Give at the footnote to the repo where all the code is available.
+We propose a simple pipeline which can be able to perform in classification and temporal localization on activities on videos.
+Moreover, the flexibility of this sequence to sequence prediction allows the proposed network to face tasks where more than a single activity is present in the video.
 
-% AMAIA: La url del repo ja l'he posat a l'abstract.
+In the future, we would like to extend the work training all the pipeline end-to-end, including the 3D-CNN and improve the accuracy accuracy obtained.
 

### 2016-10-15 paper.tex
Remove some comments and add notes
Little changes

@@
 Next, we design a network that takes a sequence of 3D-CNN-f6 features from a video, and returns a sequence of class probabilities for each element in the sequence.
-We use LSTM layers, followed with dropout with $p = .5$ and a fully connected layer with a softmax activation.
+We use LSTM layers, followed with dropout with $p = 0.5$ and a fully connected layer with a softmax activation.
 Figure~\ref{fig:global_pipeline} shows the proposed architecture.
@@
 
-where $q$ is the predicted probability distribution and $p$ the ground truth probability distribution. In our experiments, we set $\rho$ = .3.
+where $q$ is the predicted probability distribution and $p$ the ground truth probability distribution. In our experiments, we set $\rho = 0.3$.
 
-The network was trained with a 256 batch size and 20 \textit{timesteps} as input sequence.
-The optimezer function used was the RMSprop~\cite{dauphin2015rmsprop} with a learning rate set to $10^{-5}$. In total the network was trained with 100 epochs.
+The network was trained with batches of 256 samples, back-propagating the error during 20 time-steps per sample.
+The optimizer function used was the RMSprop~\cite{dauphin2015rmsprop} with a learning rate set to $10^{-5}$. In total the network was trained with 100 epochs.
 
@@
 
-% \begin{table}[h]
-% \begin{center}
-% \begin{tabular}{|l|c|c|}
-% \hline
-% \textbf{Architecture} & \textbf{mAP} & \textbf{Hit@3} \\
-% \hline\hline
-% 3 x 1024-LSTM & 0.5635 & 0.7437 \\
-% 2 x 512-LSTM & 0.5492 & 0.7364 \\
-% 1 x 512-LSTM & \bf0.5938 & \bf0.7576 \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \caption{Results for classification task comparing different deep architectures. All values with
-%          only video features on the validation dataset.}
-% \label{table:classification_by_architecture}
-% \end{table}
-%
-% \begin{table}[h]
-% \begin{center}
-% \begin{tabular}{|l|c|c|c|}
-% \hline
-% \textbf{$\gamma$} & \textbf{$k=0$} & \textbf{$k=5$} & \textbf{$k=10$} \\
-% \hline
-% \textbf{0.2} & 0.20732 & \bf0.22513 & 0.22136 \\
-% \textbf{0.3} & 0.19854 & 0.22077 & 0.22100 \\
-% \textbf{0.5} & 0.19035 & 0.21937 & 0.21302 \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \caption{mAP with an IOU threshold of $0.5$ over validation dataset. Here there is a comparison
-% between values of $k$ and $\gamma$ on post processing.}
-% \label{table:detection_postprocessing_comparison}
-% \end{table}
-% \end{multicols}
-
-% \begin{figure}
-% \centering
-% \subfloat[][]{
-% \begin{table}[h]
-% \begin{center}
-% \begin{tabular}{|l|c|c|}
-% \hline
-% \textbf{Architecture} & \textbf{mAP} & \textbf{Hit@3} \\
-% \hline\hline
-% 3 x 1024-LSTM & 0.5635 & 0.7437 \\
-% 2 x 512-LSTM & 0.5492 & 0.7364 \\
-% 1 x 512-LSTM & \bf0.5938 & \bf0.7576 \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \caption{Results for classification task comparing different deep architectures. All values with
-%          only video features on the validation dataset.}
-% \label{table:classification_by_architecture}
-% \end{table}
-% }
-% \qquad
-% \begin{table}[h]
-% \begin{center}
-% \begin{tabular}{|l|c|c|c|}
-% \hline
-% \textbf{$\gamma$} & \textbf{$k=0$} & \textbf{$k=5$} & \textbf{$k=10$} \\
-% \hline
-% \textbf{0.2} & 0.20732 & \bf0.22513 & 0.22136 \\
-% \textbf{0.3} & 0.19854 & 0.22077 & 0.22100 \\
-% \textbf{0.5} & 0.19035 & 0.21937 & 0.21302 \\
-% \hline
-% \end{tabular}
-% \end{center}
-% \caption{mAP with an IOU threshold of $0.5$ over validation dataset. Here there is a comparison
-% between values of $k$ and $\gamma$ on post processing.}
-% \label{table:detection_postprocessing_comparison}
-% \end{table}
-%
-% \end{figure}
-
 In the Figure~\ref{fig:example_results} is shown some examples of the temporal localization prediction for some instances of the dataset.
@@
 
+% ALBERTO: que més explico a les conclusions
+
 In the future, we would like to extend the work training all the pipeline end-to-end, including the 3D-CNN and improve the accuracy accuracy obtained.

### 2016-10-15 paper.tex
Fixing errors

@@
 
-The evaluation metric follow the metric used in ActivityNet Challenge to regard classification and temporal activity localization as retrieval probelm and evaluate the mAP.
-For temporal localization, a prediction is masrked correct only when it has the correct category and has IoU with ground truth instance larger than $0.5$.
+The evaluation metric follows the one used in ActivityNet Challenge with regard to classification and temporal activity localization as a retrieval problem, evaluating the mAP.
+For temporal localization, a prediction is marked correct only when it has the correct category and has IoU with ground truth instance larger than $0.5$.
 

### 2016-10-15 paper.tex
Fix erratas

@@
 The results can be found in Table~\ref{table:classification_by_architecture}.
-This results indicate that all the networks presented high learning capacity over the data ans it was obeseved a little over-fitting with the deeper architectures, obtainng the best results with a single layer of 512-LSTM cells.
+This results indicate that all the networks presented high learning capacity over the data, but a little over-fitting was observed with the deeper architectures, obtainng the best results with a single layer of 512-LSTM cells.
 
 Once the architecture has been chosen to obtain the best performance in the classification task, some experiments with different values of $k$ and $\gamma$ for the post-processing were performed.
-At Table~\ref{table:detection_postprocessing_comparison} there is the results for the temporal activity localization task, where can be seen that the effect of a mean filter to smooth helps improving the localization.
+At Table~\ref{table:detection_postprocessing_comparison} there are the results for the temporal activity localization task, where the effect of a mean smoothing filter can be seen, improving the localization.
+%there is the results for the temporal activity localization task, where can be seen that the effect of a mean filter to smooth helps improving the localization.
 
@@
 
-We propose a simple pipeline which can be able to perform in classification and temporal localization on activities on videos.
+We propose a simple pipeline which can be able to perform well in classification and temporal localization on activities on videos.
 Moreover, the flexibility of this sequence to sequence prediction allows the proposed network to face tasks where more than a single activity is present in the video.
@@
 
-In the future, we would like to extend the work training all the pipeline end-to-end, including the 3D-CNN and improve the accuracy accuracy obtained.
+In the future, we would like to extend the work training all the pipeline end-to-end, including the 3D-CNN and improve the accuracy obtained.
 

### 2016-10-15 paper.tex
Add one more contributor
Fixed erratas

@@
     \And
+    Santiago Pascual \\
+    TALP Research Center \\
+    Universitat Politècnica de Catalunya \\
+    Barcelona, Spain \\
+    \texttt{santiago.pascual@tsc.upc.edu} \\
+    \And
     Xavier Giro-i-Nieto \\
@@
     This work proposes a simple pipeline to classify and temporally localize activities in untrimmed videos.
-Our system uses features from a 3D Convolutional Neural Network (3D-CNN) as input to train a a recurrent neural network (RNN) that learns to classify video clips of 16 frames.
+Our system uses features from a 3D Convolutional Neural Network (C3D) as input to train a a recurrent neural network (RNN) that learns to classify video clips of 16 frames.
 After clip prediction, we post-process the output of the RNN to assign a single activity label to each video, and determine the temporal boundaries of the activity within the video.
@@
 Impressive progress has been reported in the recent literature for video classification~\cite{tran2014learning,tran2015deep,wang2015towards,yao2015describing}, which requires to assign a label for the input video.
-While this task is already challenging, it typically requires videos to be trimmed beforehand (i.e.
+While this task is already challenging, it has typically been explored with videos to be trimmed beforehand (i.e.
 the category is present in the entire video).
@@
 Si és així, jo directament mencionaria la challenge i la citaria.
-In order to face both these challenges at the same time, we propose a simple pipeline composed of a 3D-CNN that exploits spatial and short temporal correlations followed by a recurrent neural network which exploits long temporal correlations.
+In order to face both these challenges at the same time, we propose a simple pipeline composed of a 3D-CNN that exploits spatial and short temporal correlations, followed by a recurrent neural network which exploits long temporal correlations.
 
@@
 
-Later on, 3D-CNNs were proposed in ~\cite{tran2014learning}, which were able to exploit short temporal correlations between frames and have demonstrated to work remarkably well for video classification~\cite{tran2014learning,tran2015deep}.
-3D-CNNs have also been used for temporal detection in~\cite{shoutemporal}, where multi-stage 3D-CNN architecture is used to classify video segment proposals.
+Later on, 3D-CNNs were proposed in~\cite{tran2014learning} (known as C3D), which were able to exploit short temporal correlations between frames and have demonstrated to work remarkably well for video classification~\cite{tran2014learning,tran2015deep}.
+C3D have also been used for temporal detection in~\cite{scnn_shou_wang_chang_cvpr16}, where multi-stage C3D architecture is used to classify video segment proposals.
 
@@
 
-We use the 3D-CNN model proposed in~\cite{tran2014learning} to extract features for all videos in the database.
-We split the videos in 16-frame clips and resize them to 171$\times$128 to fit the original model's desired input.
+We use the C3D model proposed in~\cite{tran2014learning} to extract features for all videos in the database.
+We split the videos in 16-frames clips and resize them to 171$\times$128 to fit the input of the C3D model.
 Features from the second fully connected layer (fc6) are extracted for each video clip.
@@
 \label{sec:architecture}
-Next, we design a network that takes a sequence of 3D-CNN-f6 features from a video, and returns a sequence of class probabilities for each element in the sequence.
-We use LSTM layers, followed with dropout with $p = 0.5$ and a fully connected layer with a softmax activation.
+We design a network that processes a sequence of C3D-f6 features from a video, and returns a sequence of class probabilities for each 16-frames clip.
+We use LSTM layers, trained with dropout with $p = 0.5$ and a fully connected layer with a softmax activation.
 Figure~\ref{fig:global_pipeline} shows the proposed architecture.
-Different configurations of the number of LSTM layers and the number of cells have been tested and will be reviewed in the following sections.
+Different configurations of the number of LSTM layers $N$ and the number of cells $c$ have been tested and are compared in Section~\ref{sec:resultats}.
+The recurrent network have the following architecture: \texttt{input(4096) - dropout(.5) - N $\times$ lstm(c) - dropout(.5) - softmax(K+1)} where $K$ is the number of activity classes at the dataset.
 
@@
 
-%The recurrent network have the following architecture: \texttt{input(4096) - dropout(.5) - N $\times$ lstm(c) - dropout(.5) - softmax(K+1)}.
-
 %\paragraph{Training.}
@@
 \subsection{Post-Processing}
-Given a video, the prediction of our model is sequence of class probabilities for each 16-frame video clip.
-From this output, we need to be able to predict the activity  and temporally localize it.
-We post-process the network's output to achieve that goal.
-First, to obtain the activity prediction for the whole video, we simply compute the mean over all video clips in the video.
-We then take the class with maximum predicted probability as the predicted class.
+Given a video, the prediction of our model is sequence of class probabilities for each 16-frame video clip. This output is post-processed to predict the activity class and temporally localize it.
+First, to obtain the activity prediction for the whole video, we compute the average of the class probabilities over all video clips in the video.
+We consider the class with maximum predicted probability as the predicted class.
 
@@
 
-To obtain the temporal localization of the predicted activity, we first apply a mean filter of $k$ samples to the predicted sequence to smooth the values through time (see equation~\ref{eq:smooth}).
-Then, the probability of activity (vs no activity) is computed for all samples of the sequence, being the activity probability the sum of all activity probabilities, and the no activity probability, the one assigned to the background class.
-Finally, a threshold $\gamma$ is set and all clips with probability higher than $\gamma$ are considered as part of the detected temporal segment for the previously assigned activity.
+To obtain the temporal localization of the predicted activity class, we first apply a mean filter of $k$ samples to the predicted sequence to smooth the values through time (see equation~\ref{eq:smooth}).
+Then, the probability of \textit{activity} (vs \textit{no activity}) is predicted for each 16-frames clip, being the \textit{activity} probability the sum of all probabilities of activity classes, and the \textit{no activity} probability, the one assigned to the background class.
+Finally, only those clips with an \textit{activity} probability over a threshold $\gamma$ are kept and labeled with the previously predicted class.
+Notice that, in our dataset, each video can only contain video segments of the same activity class.
+%a threshold $\gamma$ is set and all clips with probability higher than $\gamma$ are considered as part of the detected temporal segment for the previously assigned activity.
 
@@
 \subsection{Results}
+\label{sec:resultats}
 
@@
 
-In the future, we would like to extend the work training all the pipeline end-to-end, including the 3D-CNN and improve the accuracy obtained.
+In the future, we would like to extend the work training all the pipeline end-to-end, including the C3D and improve the accuracy obtained.
 

### 2016-10-15 paper.tex
Things

@@
 We propose a simple pipeline which can be able to perform well in classification and temporal localization on activities on videos.
-Moreover, the flexibility of this sequence to sequence prediction allows the proposed network to face tasks where more than a single activity is present in the video.
+Moreover, the flexibility of this network performing a sequence to sequence prediction allows it to face tasks where more than a single activity is present in the video.
 
-% ALBERTO: que més explico a les conclusions
+% ALBERTO: que més explico a les conclusions???
 

### 2016-10-15 paper.tex
Update on Overleaf.

@@
 Impressive progress has been reported in the recent literature for video classification~\cite{tran2014learning,tran2015deep,wang2015towards,yao2015describing}, which requires to assign a label for the input video.
-While this task is already challenging, it has typically been explored with videos to be trimmed beforehand (i.e.
-the category is present in the entire video).
+While this task is already challenging, it has typically been explored with videos to be trimmed beforehand.
 However, a video classification system should be able to recognize activities in untrimmed videos, and find the temporal segments in which they appear.
@@
 Several works in the literature have used 2D-CNNs to exploit the spatial correlations between frames of a video by combining their outputs using different strategies~\cite{gkioxari2015contextual,yeung2015end,ballas2015delving}.
-Others have tried using the optical flow as an additional input to the 2D-CNN videos~\cite{wang2015towards}, which provides information of the temporal correlations.
+Others have tried using the optical flow as an additional input to the 2D-CNNN~\cite{wang2015towards}, which provides information of the temporal correlations.
 % AMAIA: Tot això s'ha de revisar...
@@
 For temporal activity detection, recent works have proposed the usage of Long Short-Term Memory units (LSTM)~\cite{hochreiter1997long}.
-LSTMs are a type of RNNs that is able to better exploit long and short temporal correlations in sequences, which makes them suitable for video applications.
+LSTMs are a type of RNNs that are able to better exploit long and short temporal correlations in sequences, which makes them suitable for video applications.
 LSTMs have been used alongside CNNs for video classification~\cite{yao2015describing} and activity localization in videos~\cite{yeung2015every}. 
+Our proposed network is inspired by this solutions using the C3D that so well perform in video, and also a RNN which will exploit long temporal correlations and allows to predict a sequence.
 
@@
 
-\subsection{Recurrent Neural Network}
+\subsection{Architecture}
 \label{sec:architecture}
@@
 Different configurations of the number of LSTM layers $N$ and the number of cells $c$ have been tested and are compared in Section~\ref{sec:resultats}.
-The recurrent network have the following architecture: \texttt{input(4096) - dropout(.5) - N $\times$ lstm(c) - dropout(.5) - softmax(K+1)} where $K$ is the number of activity classes at the dataset.
+Our proposed system has the following architecture: \texttt{input(4096) - dropout(0.5) - N $\times$ lstm(c) - dropout(.5) - softmax(K+1)} where $K$ is the number of activity classes at the dataset.
 
@@
 
-The network was trained with batches of 256 samples, back-propagating the error during 20 time-steps per sample.
-The optimizer function used was the RMSprop~\cite{dauphin2015rmsprop} with a learning rate set to $10^{-5}$. In total the network was trained with 100 epochs.
+The network was trained for 100 epochs, with a batch size of 256, where each sample in the minibatch is a sequence of 20 16-frame video clips.
+We use RMSprop~\cite{dauphin2015rmsprop} with a learning rate set to $10^{-5}$.
 
@@
 
-The evaluation metric follows the one used in ActivityNet Challenge with regard to classification and temporal activity localization as a retrieval problem, evaluating the mAP.
+We evaluate our methods with the mean average precision (mAP), which is the metric used in ActivityNet Challenge with regard to classification and temporal activity localization as a retrieval problem.
 For temporal localization, a prediction is marked correct only when it has the correct category and has IoU with ground truth instance larger than $0.5$.
@@
 
-The first results are related with the network architecture.
-It has been tested with different number of layers and different number of cells having all the layers the same number of cells.
-The results can be found in Table~\ref{table:classification_by_architecture}.
-This results indicate that all the networks presented high learning capacity over the data, but a little over-fitting was observed with the deeper architectures, obtainng the best results with a single layer of 512-LSTM cells.
+Results in Table~\ref{table:classification_by_architecture} show the performance of different network configurations.
+We experimented with different number of LSTM layers and different number of cells.
+These results indicate that all the networks presented high learning capacity over the data, but over-fitting was observed with the deeper architectures, obtaining the best results with a single layer of 512-LSTM cells.
 
 Once the architecture has been chosen to obtain the best performance in the classification task, some experiments with different values of $k$ and $\gamma$ for the post-processing were performed.
-At Table~\ref{table:detection_postprocessing_comparison} there are the results for the temporal activity localization task, where the effect of a mean smoothing filter can be seen, improving the localization.
-%there is the results for the temporal activity localization task, where can be seen that the effect of a mean filter to smooth helps improving the localization.
-
-In the Figure~\ref{fig:example_results} is shown some examples of the temporal localization prediction for some instances of the dataset.
-It can be seen how the predictions are continuous and smooth and mostly overlaps with the ground truth instances.
+Table~\ref{table:detection_postprocessing_comparison} shows results for the temporal activity localization task, where the effect of a mean smoothing filter can be seen, improving the localization.
+Figure~\ref{fig:example_results} shows some examples of the temporal localization prediction for some instances of the dataset.
+It can be seen how the predictions are continuous and smooth.
+% AMAIA: No sé si els exemples de la figura son els millors...no en tens algun on la detecció estigui bé pero la classe no? o al reves? No en vas posar algun a la presentacio de la defensa?
 
@@
 
-We propose a simple pipeline which can be able to perform well in classification and temporal localization on activities on videos.
-Moreover, the flexibility of this network performing a sequence to sequence prediction allows it to face tasks where more than a single activity is present in the video.
+In this paper we propose a simple pipeline for both classification and temporal localization of activities in videos.
+Our system achieves competitive results on both tasks.
+The sequence to sequence nature of the proposed network offers flexibility to extend it to face more challenging tasks in video processing, e.g.
+where more than a single activity is present in the video.
+Future work will address end to end training of the model (3D-CNN + RNN), to learn better feature representations suitable for the dataset.
 
 % ALBERTO: que més explico a les conclusions???
-
-In the future, we would like to extend the work training all the pipeline end-to-end, including the C3D and improve the accuracy obtained.
 

### 2016-10-15 paper.tex
Change one figure
Update on Overleaf.

@@
 LSTMs have been used alongside CNNs for video classification~\cite{yao2015describing} and activity localization in videos~\cite{yeung2015every}.
-Our proposed network is inspired by this solutions using the C3D that so well perform in video, and also a RNN which will exploit long temporal correlations and allows to predict a sequence.
+
+In this paper, we combine the capabilities of both 3D-CNNs and RNNs into a single framework.
+This way, we design a simple network that takes a sequence of video features from the C3D model~\cite{tran2014learning} as input to a RNN and is able to classify each one of them into an activity category.
 
@@
 We design a network that processes a sequence of C3D-f6 features from a video, and returns a sequence of class probabilities for each 16-frames clip. 
-We use LSTM layers, trained with dropout with $p = 0.5$ and a fully connected layer with a softmax activation.
-Figure~\ref{fig:global_pipeline} shows the proposed architecture.
+We use LSTM layers, trained with dropout with probability $p = 0.5$ and a fully connected layer with a softmax activation. Figure~\ref{fig:global_pipeline} shows the proposed architecture. 
 Different configurations of the number of LSTM layers $N$ and the number of cells $c$ have been tested and are compared in Section~\ref{sec:resultats}. 
@@
 
-To obtain the temporal localization of the predicted activity class, we first apply a mean filter of $k$ samples to the predicted sequence to smooth the values through time (see equation~\ref{eq:smooth}).
+To obtain the temporal localization of the predicted activity class, we first apply a mean filter of $k$ samples to the predicted sequence to smooth the values through time (see Equation~\ref{eq:smooth}).
 Then, the probability of \textit{activity} (vs \textit{no activity}) is predicted for each 16-frames clip, being the \textit{activity} probability the sum of all probabilities of activity classes, and the \textit{no activity} probability, the one assigned to the background class.
 Finally, only those clips with an \textit{activity} probability over a threshold $\gamma$ are kept and labeled with the previously predicted class.
-Notice that, in our dataset, each video can only contain video segments of the same activity class.
+Notice that, for each video, all predicted temporal detections are activity class.
 %a threshold $\gamma$ is set and all clips with probability higher than $\gamma$ are considered as part of the detected temporal segment for the previously assigned activity.
@@
 
-We evaluate our methods with the mean average precision (mAP), which is the metric used in ActivityNet Challenge with regard to classification and temporal activity localization as a retrieval problem.
-For temporal localization, a prediction is marked correct only when it has the correct category and has IoU with ground truth instance larger than $0.5$.
+We evaluate our models using the metrics proposed in ActivityNet Challenge.
+For video classification, we use mean average precision (mAP) and Hit@3.
+For temporal localization, a prediction is marked correct only when it has the correct category and has IoU with ground truth instance larger than $0.5$, and mAP is used to evaluate the performance over the entire dataset.
 
@@
         \vspace{.2cm}
-        \caption{mAP with an IOU threshold of $0.5$ comparing between values of $k$ and $\gamma$ on post-processing.}
+        \caption{mAP with an IoU threshold of $0.5$ comparing between values of $k$ and $\gamma$ on post-processing.}
         \label{table:detection_postprocessing_comparison}
@@
 
-Results in Table~\ref{table:classification_by_architecture} show the performance of different network configurations.
-We experimented with different number of LSTM layers and different number of cells.
-These results indicate that all the networks presented high learning capacity over the data, but over-fitting was observed with the deeper architectures, obtaining the best results with a single layer of 512-LSTM cells.
+Table~\ref{table:classification_by_architecture} shows the performance of different network architectures.
+We tested configurations with different number of LSTM layers and different number of cells.
+These results indicate that all the networks presented high learning capacity over the data, but some over-fitting was observed with the deeper architectures, obtaining the best results with a single layer of 512-LSTM cells.
 
-Once the architecture has been chosen to obtain the best performance in the classification task, some experiments with different values of $k$ and $\gamma$ for the post-processing were performed.
-Table~\ref{table:detection_postprocessing_comparison} shows results for the temporal activity localization task, where the effect of a mean smoothing filter can be seen, improving the localization.
-Figure~\ref{fig:example_results} shows some examples of the temporal localization prediction for some instances of the dataset.
-It can be seen how the predictions are continuous and smooth.
+Fixing the architecture, we performed experiments for the temporal detection task using different values of $k$ and $\gamma$ in the post-processing stage.
+Table~\ref{table:detection_postprocessing_comparison} shows results for the temporal activity localization task, where the effect of a mean smoothing filter can be seen, improving the localization performance.
+Figure~\ref{fig:example_results} shows some examples of the temporal localization prediction for some instances of the dataset, showing continuous and smooth segments.
 % AMAIA: No sé si els exemples de la figura son els millors...no en tens algun on la detecció estigui bé pero la classe no? o al reves? No en vas posar algun a la presentacio de la defensa?
-
+% ALBERTO: Ja he ficat un exemple que passa el que tu dius
+% AMAIA: Vist
 \begin{figure}[ht]
@@
 \includegraphics[width=1\linewidth]{img/activity_temporal_localization_8.png}
-\includegraphics[width=1\linewidth]{img/activity_temporal_localization_11.png}
+\includegraphics[width=1\linewidth]{img/activity_temporal_localization_55.png}
 \includegraphics[width=1\linewidth]{img/activity_temporal_localization_20.png}
-\includegraphics[width=1\linewidth]{img/activity_temporal_localization_35.png}
-
+%\includegraphics[width=1\linewidth]{img/activity_temporal_localization_35.png}
 \caption{Global architecture of the proposed pipeline.}
@@
 \end{figure}
+
 % AMAIA: Crec que amb una secció on expliquis tots els experiments ja n'hi ha prou. Li he posat el nom de 'Results'

### 2016-10-15 paper.tex
Add classification example

@@
 Table~\ref{table:detection_postprocessing_comparison} shows results for the temporal activity localization task, where the effect of a mean smoothing filter can be seen, improving the localization performance.
-Figure~\ref{fig:example_results} shows some examples of the temporal localization prediction for some instances of the dataset, showing continuous and smooth segments.
+Figures~\ref{fig:example_results_detect} and~\ref{fig:example_results_classification} shows some examples of classification and temporal localization prediction for some instances of the dataset, showing continuous and smooth segments.
 % AMAIA: No sé si els exemples de la figura son els millors...no en tens algun on la detecció estigui bé pero la classe no? o al reves? No en vas posar algun a la presentacio de la defensa?
@@
 %\includegraphics[width=1\linewidth]{img/activity_temporal_localization_35.png}
-\caption{Global architecture of the proposed pipeline.}
-\label{fig:example_results}
+\caption{Examples of temporal activity localization predictions.}
+\label{fig:example_results_detect}
+\end{figure}
+
+\begin{figure}[h]
+\centering
+\begin{subfigure}[b]{.4\textwidth}
+  \texttt{Video ID: ArzhjEk4j\_Y \\
+  Activity: Building sandcastles \\
+  \\
+  Prediction: \\
+  0.7896	Building sandcastles \\
+  0.0073	Doing motocross \\
+  0.0049	Beach soccer \\}
+\end{subfigure}%
+\begin{subfigure}[b]{.6\textwidth}
+  \centering
+\includegraphics[width=0.95\linewidth]{img/results_visualization_classification_1}
+\end{subfigure}
+\caption{Example of activity classification.}
+\label{fig:example_results_classification}
 \end{figure}

### 2016-10-15 paper.tex
Update on Overleaf.

@@
 Table~\ref{table:detection_postprocessing_comparison} shows results for the temporal activity localization task, where the effect of a mean smoothing filter can be seen, improving the localization performance.
-Figures~\ref{fig:example_results_detect} and~\ref{fig:example_results_classification} shows some examples of classification and temporal localization prediction for some instances of the dataset, showing continuous and smooth segments.
+Figures~\ref{fig:example_results_detect} and~\ref{fig:example_results_classification} show some examples of classification and temporal localization prediction for some instances of the dataset.
 % AMAIA: No sé si els exemples de la figura son els millors...no en tens algun on la detecció estigui bé pero la classe no? o al reves? No en vas posar algun a la presentacio de la defensa?

### 2016-10-15 paper.tex
Add more figure

@@
 \centering
-\begin{subfigure}[b]{.4\textwidth}
+\begin{subfigure}[b]{.5\textwidth}
+    \includegraphics[width=0.9\linewidth]{img/results_visualization_classification_1}
     \texttt{Video ID: ArzhjEk4j\_Y \\
-  Activity: Building sandcastles \\
+    Ground Truth: Building sandcastles \\
     \\
@@
 \end{subfigure}%
-\begin{subfigure}[b]{.6\textwidth}
-  \centering
-\includegraphics[width=0.95\linewidth]{img/results_visualization_classification_1}
+\begin{subfigure}[b]{.5\textwidth}
+    \includegraphics[width=0.9\linewidth]{img/results_visualization_classification_4}
+    \texttt{Video ID: VrNHEv6aR38 \\
+    Ground Truth: Playing water polo \\
+    \\
+    Prediction: \\
+    0.7645	Playing water polo \\
+    0.2018	Swimming \\
+    0.0065	Springboard diving\\}
 \end{subfigure}
-\caption{Example of activity classification.}
+
+\caption{Examples of activity classification.}
 \label{fig:example_results_classification}

### 2016-10-15 paper.tex
New figure

@@
 \begin{subfigure}[b]{.5\textwidth}
-    \includegraphics[width=0.9\linewidth]{img/results_visualization_classification_4}
-    \texttt{Video ID: VrNHEv6aR38 \\
-    Ground Truth: Playing water polo \\
+    \includegraphics[width=0.9\linewidth]{img/results_visualization_classification_2}
+    \texttt{Video ID: AimG8xzchfI \\
+	Activity: Curling \\
     \\
     Prediction: \\
-    0.7645	Playing water polo \\
-    0.2018	Swimming \\
-    0.0065	Springboard diving\\}
+    0.3843	Shoveling snow \\
+    0.1181	Ice fishing \\
+    0.0633	Waterskiing \\}
 \end{subfigure}
